Computer Science House Constitution

### 2015-12-17 articles.tex
Added Alternatve Vote to voting options.

\asection{Types of Voting}
\asubsection{Balloted Vote}
\asubsubsection{Method of Vote} 
Votes are cast on paper ballots, which provide a means to indicate every possible option in the vote. A ballot is then distributed to each House member eligible to cast a vote and collected in the designated ballot box for a pre-specified length of time. At the end of the voting period, the person chairing the vote collects the ballots, closing the voting period. The Vote Counters then tally the results.
\asubsubsection{Voting Period} 
For constitutional modification, candidate selection, and officer removal votes, the voting period must be at least forty-eight (48) hours in length. For any other type of vote, the voting period must be at least twenty-four (24) hours. The minimum length of the voting period may be explicitly lengthed, but never shortened, in the text describing the actual vote.
\asubsection{Immediate Vote}
\asubsubsection{Method of Vote} 
The person chairing the vote will state all possible ways to vote, then call out each possibility one at a time. The chairing member will count the number of members casting their immediate vote for that possibility.
\asubsubsection{Voting Period} 
An immediate vote lasts as long as it takes for all votes to be tallied.
\asubsection{Secret Immediate Vote}
\asubsubsection{Method of Vote} 
The person chairing the vote will state all possible ways to vote, then call out each possibility one at a time. Votes are kept anonymous. The chairing member and Vote Counters will count the number of members casting their immediate vote for that possibility.
\asubsubsection{Voting Period}
A secret immediate vote lasts as long as it takes for all votes to be tallied.
\asubsection{Batch Vote}
When a Batch Vote is called for by the chair, a subset of the voting docket may be amended to a single vote. A Two-Thirds Immediate Vote is required to allow a Batch Vote to take place. If the call for Batch Vote passes, the subset may then be voted on, otherwise the docket remains unchanged.

>>>>

\asection{Types of Voting}
\asubsection{Alternative Vote}
\asubsubsection{Method of Vote}
Each voter has one vote, but rather than an X, they put a '1' by their first choice a '2' by their second choice, and so on, until they no longer wish to express any further preferences or run out of candidates.

Candidates are elected outright if they gain more than half the votes as first preferences. If not, the candidate who lost (the one with least first preferences) is eliminated and their votes move to the second preference marked on the ballot papers. This process continues until one candidate has half of the votes and is elected.
\asubsubsection{Voting Period} 
For constitutional modification, candidate selection, and officer removal votes, the voting period must be at least forty-eight (48) hours in length. For any other type of vote, the voting period must be at least twenty-four (24) hours. The minimum length of the voting period may be explicitly lengthed, but never shortened, in the text describing the actual vote.
\asubsection{Balloted Vote}
\asubsubsection{Method of Vote} 
Votes are cast on paper ballots, which provide a means to indicate every possible option in the vote. A ballot is then distributed to each House member eligible to cast a vote and collected in the designated ballot box for a pre-specified length of time. At the end of the voting period, the person chairing the vote collects the ballots, closing the voting period. The Vote Counters then tally the results.
\asubsubsection{Voting Period} 
For constitutional modification, candidate selection, and officer removal votes, the voting period must be at least forty-eight (48) hours in length. For any other type of vote, the voting period must be at least twenty-four (24) hours. The minimum length of the voting period may be explicitly lengthed, but never shortened, in the text describing the actual vote.
\asubsection{Immediate Vote}
\asubsubsection{Method of Vote} 
The person chairing the vote will state all possible ways to vote, then call out each possibility one at a time. The chairing member will count the number of members casting their immediate vote for that possibility.
\asubsubsection{Voting Period} 
An immediate vote lasts as long as it takes for all votes to be tallied.
\asubsection{Secret Immediate Vote}
\asubsubsection{Method of Vote} 
The person chairing the vote will state all possible ways to vote, then call out each possibility one at a time. Votes are kept anonymous. The chairing member and Vote Counters will count the number of members casting their immediate vote for that possibility.
\asubsubsection{Voting Period}
A secret immediate vote lasts as long as it takes for all votes to be tallied.
\asubsection{Batch Vote}
When a Batch Vote is called for by the chair, a subset of the voting docket may be amended to a single vote. A Two-Thirds Immediate Vote is required to allow a Batch Vote to take place. If the call for Batch Vote passes, the subset may then be voted on, otherwise the docket remains unchanged.
